---
title: "Flexmix"
author: "Garima Sood"
date: "August 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
library("flexmix")
library(nnet)
library(mlr) 
library(DescTools)
library(e1071)
library(class)
library(psych)
library(randomForest)
```


## Load test and train

```{r load data}
#train_dat <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/PCA/mol_PCA_train.csv')
#head(train_dat)

#test_dat <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/PCA/mol_PCA_test.csv')
#head(test_dat)

#trna <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/RNA/trna_BRCA_s01_unique.csv')
#head(trna)

#selectedrna <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/RNA/select_rna.txt')
#rownames(selectedrna) <- selectedrna$participant

additional_features <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/rna_mirna_meth_clin.csv')
rownames(additional_features) <- additional_features[,1] 
additional_features <- additional_features[,-1]
additional_features$menopause_status <- ifelse(additional_features$menopause_status==0,"NA",additional_features$menopause_status)
additional_features$menopause_status <- as.factor(additional_features$menopause_status)
additional_features <- additional_features[, -which(names(additional_features) %in% c('anatomic_neoplasm_subdivisions', 'ajcc_pathologic_tumor_stage','menopause_status'))]

#yy <- lapply(colnames(trna), function(x) strsplit(as.character(x),"\\.")[[1]][1])
#brcagennes <- c('ENSG00000139618', 'ENSG00000012048')

#rna_genes <- trna[, which(yy %in% c('ENSG00000139618', 'ENSG00000012048'))]
#rownames(rna_genes) <- trna$participant
#write.csv(rna_genes, 'rna_genes.csv')

#rna_genes <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/rna_genes.csv')
cnv <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/cnvselected.csv')
rownames(cnv) <- cnv[,1] 
cnv <- cnv[,-1]
#rownames(rna_genes) <- rna_genes$X
#rna_genes <- rna_genes[,-1]

train_id <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/train_id.csv')
test_id <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/test_id.csv')

train_id <- data.frame(train_id[,2])
colnames(train_id) <- 'participant'

test_id <-  data.frame(test_id[,2])
colnames(test_id) <- 'participant'

clin_dat <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Drug/Drug_BRCA_unique_freq.csv')
rownames(clin_dat) <- clin_dat[,1]
clin_dat <- clin_dat[,-1]

mirna_genes <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/mirna_genes.csv')
rownames(mirna_genes) <- mirna_genes[,1]
mirna_genes <- mirna_genes[,-1]

final_sel <- read.csv('C:/Users/garim/Documents/Capstone/Codes/Flexmix/top_10_ohe_drug_freq_v2.csv') 
rownames(final_sel) <- final_sel$X
final_sel <- final_sel[,-1]

smp_size <- floor(0.75 * nrow(final_sel))

## set the seed to make your partition reproducible
set.seed(500)
train_ind <- sample(seq_len(nrow(final_sel)), size = smp_size)

train <- final_sel[train_ind, ]
test <- final_sel[-train_ind, ]


#train <- merge(train_id,rna_genes, by.x = 'participant', by.y = 0)
train <- merge(train_id,final_sel, by.x = 'participant', by.y = 0)
train <- merge(train, cnv, by.x = 'participant', by.y = 0)
train <- merge(train, additional_features, by.x = 'participant', by.y = 0)
train <- merge(train, mirna_genes, by.x = 'participant', by.y = 0)
rownames(train) <- train[,1]
train <- train[,-1]
 
#test <- merge(test_id,rna_genes, by.x = 'participant', by.y = 0)
test <- merge(test_id,final_sel, by.x = 'participant', by.y = 0)
test <- merge(test, cnv, by.x = 'participant', by.y = 0)
test <- merge(test, additional_features, by.x = 'participant', by.y = 0)
test <- merge(test, mirna_genes, by.x = 'participant', by.y = 0)
rownames(test) <- test[,1]
test <- test[,-1]

train$PFIbucket <- as.factor(ifelse(train$PFI.time<795,0,1))
test$PFIbucket <- as.factor(ifelse(test$PFI.time<795,0,1))
 
train$PFIbucket <- as.factor(ifelse(train$PFI.time<575,1,ifelse(train$PFI.time<1450,2,3)))

test$PFIbucket <- as.factor(ifelse(test$PFI.time<575,1,ifelse(test$PFI.time<1450,2,3)))
```

```{r}
library(classInt)
classIntervals(train$PFI.time, 3)
x <- classIntervals(final_sel$PFI.time, 3, style = 'quantile')
x

```


```{r}
selectedcol = colnames(selectedrna)
trna <- merge(train_dat,selectedrna, by = 'participant')
trna <- trna[selectedcol]
trna = trna[,-ncol(trna)]
#clustrna = cbind(trna, 'cluster'=clust)

testrna <- merge(test_dat,selectedrna, by = 'participant')
testrna <- testrna[selectedcol]
testrna = testrna[,-ncol(testrna)]
#clustestrna = cbind(testrna, 'cluster'=clusters(selected_model, newdata = test))
```

## Subsetting test and train data based on desired variables

```{r subset data}
train  = train_dat[,c(2:9,109:122)]
test  = test_dat[,c(2:9,109:122)]

#train = train[,-which(names(train) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI'))]
#test = test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI'))]

```

```{r}
gamma_reg <- glm(PFI.time ~ ., data = train, family = Gamma(link = 'log'))

summary(gamma_reg)     
RMSE(predict(gamma_reg, train, type = 'response'), train$PFI.time)
RMSE(predict(gamma_reg, test, type = 'response'), test$PFI.time)
```

```{r}
pois_reg <- glm(PFI.time ~ ., data = train, family = poisson(link = 'log'))

summary(pois_reg)     
RMSE(predict(pois_reg, train, type = 'response'), train$PFI.time)
RMSE(predict(pois_reg, test, type = 'response'), test$PFI.time)
```

```{r}
norm_reg <- lm(PFI.time ~ ., data = train)

summary(norm_reg)     
RMSE(predict(norm_reg, train, type = 'response'), train$PFI.time)
RMSE(predict(norm_reg, test, type = 'response'), test$PFI.time)
```

## Fitting a step model on the train data

```{r model}
FittedBin <- initFlexmix(PFI.time ~ ., data = train, k=1:3,  nrep =12, model = list(FLXMRglm(family="poisson")))

FittedBin
```

```{r}
predictedtrain = predict(FittedBin@models$`1`,train[,-which(names(test) %in% c('PFI.time'))])

predicted = predict(FittedBin@models$`1`,test[,-which(names(test) %in% c('PFI.time'))])

ypred2 = predictedtrain$Comp.1
ytest2 = predicted$Comp.1
sqrt(mean((train$PFI.time-ypred2)^2))
sqrt(mean((test$PFI.time-ytest2)^2))
```

```{r}
summary(refit(FittedBin@models$`1`))

```


```{r}
predictedtrain = predict(FittedBin@models$`2`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`2`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])
clusters(FittedBin@models$`2`,test)
ypred2 =  ifelse(clusters(FittedBin@models$`2`,train)==1,predictedtrain$Comp.1,predictedtrain$Comp.2)
ytest2 = ifelse(clusters(FittedBin@models$`2`,test)==1,predicted$Comp.1,predicted$Comp.2)
sqrt(mean((test$PFI.time-ytest2)^2))
sqrt(mean((train$PFI.time-ypred2)^2))
```

```{r}
summary(refit(FittedBin@models$`2`))
```

```{r}

polufxn <- svm(cluster~.,cbind(train[,-which(colnames(train) %in% 'PFI.time')], 
            "cluster" = as.factor(clusters(FittedBin@models$`2`, train))), kernel = 'sigmoid')
table( clusters(FittedBin@models$`2`, train), predict(polufxn, train[,-which(colnames(train) %in% 'PFI.time')]))
sum(clusters(FittedBin@models$`2`, train) ==predict(polufxn, train[,-which(colnames(train) %in% 'PFI.time')]))/ length(clusters(FittedBin@models$`3`, train))

table( clusters(FittedBin@models$`2`, test), predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')]))
sum(clusters(FittedBin@models$`2`, test) ==predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')]))/ length(clusters(FittedBin@models$`2`, test))

```

```{r}
train_clus = cbind(train[,-which(colnames(train) %in% 'PFI.time')], 'cluster' = (clusters(FittedBin@models$`2`,train)))
test_clus = cbind(test[,-which(colnames(test) %in% 'PFI.time')], 'cluster' = (clusters(FittedBin@models$`2`,newdata = test)))

knnfxn <- knn(train =train[,-which(colnames(train) %in% 'PFI.time')], 
              test = test[,-which(colnames(test) %in% 'PFI.time')],
              cl= as.factor(train_clus$cluster), k = 20)

table( clusters(FittedBin@models$`2`, test),knnfxn)
sum(clusters(FittedBin@models$`2`, test) ==knnfxn)/ length(clusters(FittedBin@models$`2`, test))
```


```{r test fit}
check_test= predict(FittedBin@models$`2`, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test = predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')])

ypredtest = cbind("comp1"=check_test$Comp.1, "comp2"=check_test$Comp.2, clust_test)
ytest = ifelse(ypredtest[,3]==1, ypredtest[,1], ypredtest[,2])
ytest2 = ifelse(knnfxn==1, ypredtest[,1], ypredtest[,2])
RMSE(ytest, test$PFI.time)
```

```{r}
plot(test$PFI.time, ytest)
plot(test$PFI.time, test$PFI.time-ytest)
```



```{r}
data1 <- cbind(test[,-which(names(test) %in% c('PFI.time'))], 'PFI.time' = as.integer(predicted$Comp.1))
data2 <- cbind(test[,-which(names(test) %in% c('PFI.time'))], 'PFI.time' = as.integer(predicted$Comp.2))
clust1 <- clusters(FittedBin@models$`2`, newdata = data1)
clust2 <- clusters(FittedBin@models$`2`, newdata = data2)
cbind(clust1,clust2,'actual'=clusters(FittedBin@models$`2`, newdata = test))

```


```{r}
predictedtrain = predict(FittedBin@models$`3`,train[,-which(names(train) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`3`,newdata = test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])
table(clusters(FittedBin@models$`3`,train))
ypred2 =  ifelse(clusters(FittedBin@models$`3`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`3`,train)==2,predictedtrain$Comp.2,predictedtrain$Comp.3))
ytest2 = ifelse(clusters(FittedBin@models$`3`,test)==1,predicted$Comp.1,ifelse(clusters(FittedBin@models$`3`,test)==2, predicted$Comp.2, predicted$Comp.3))
sqrt(mean((test$PFI.time-ytest2)^2))
sqrt(mean((train$PFI.time-ypred2)^2))
```



```{r}
summary(refit(FittedBin@models$`3`))
```

```{r}
write.csv(cbind(train$X0, "cluster" = clusters(FittedBin@models$`3`, train)),'clust_3_assignemt.csv')

```

```{r}

polufxn <- svm(cluster~.,cbind(train[,-which(colnames(train) %in% 'PFI.time')], 
            "cluster" = as.factor(clusters(FittedBin@models$`3`, train))), kernel = 'radial')
table( clusters(FittedBin@models$`3`, train), predict(polufxn, train[,-which(colnames(train) %in% 'PFI.time')]))
sum(clusters(FittedBin@models$`3`, train) ==predict(polufxn, train[,-which(colnames(train) %in% 'PFI.time')]))/ length(clusters(FittedBin@models$`3`, train))

table( clusters(FittedBin@models$`3`, test), predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')]))
sum(clusters(FittedBin@models$`3`, test) ==predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')]))/ length(clusters(FittedBin@models$`3`, test))

```


```{r}
train_clus = cbind(train[,-which(colnames(train) %in% 'PFI.time')], 'cluster' = (clusters(FittedBin@models$`3`,train)))
test_clus = cbind(test[,-which(colnames(test) %in% 'PFI.time')], 'cluster' = (clusters(FittedBin@models$`3`,newdata = test)))

knnfxn <- knn(train =train[,-which(colnames(train) %in% 'PFI.time')], 
              test = test[,-which(colnames(test) %in% 'PFI.time')],
              cl= as.factor(train_clus$cluster), k = 20)

table( clusters(FittedBin@models$`3`, test),knnfxn)
sum(clusters(FittedBin@models$`3`, test) ==knnfxn)/ length(clusters(FittedBin@models$`3`, test))
```

```{r test fit}
check_test= predict(FittedBin@models$`3`, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test = predict(polufxn, test[,-which(colnames(test) %in% 'PFI.time')])

ypredtest = cbind("comp1"=check_test$Comp.1, "comp2"=check_test$Comp.2, "comp3"=check_test$Comp.3, clust_test)
ytest = ifelse(ypredtest[,4]==1, ypredtest[,1], ifelse(ypredtest[,4]==2, ypredtest[,2],ypredtest[,3]))
ytest2 = ifelse(knnfxn==1, ypredtest[,1], ifelse(knnfxn==2, ypredtest[,2],ypredtest[,3]))
RMSE(ytest, test$PFI.time)
```

```{r}
plot(test$PFI.time, ytest)
plot(test$PFI.time, test$PFI.time-ytest)
```

```{r model}
FittedBincat <- flexmix(cbind(PFIbucket==0,PFIbucket==1) ~ ENSG00000012048.18+ ENSG00000139618.13+ Cyclophosphamide + Doxorubicin+ Tamoxifen+ Anastrozole+ Paclitaxel+ Docetaxel+ Fluorouracil+ Trastuzumab+ Letrozole+ Exemestane +Epirubicin+ Carboplatin+ Methotrexate+ chr17.41000001.42000000+ chr13.32000001.33000000,  data = train[,-which(colnames(train) %in% 'PFI.time')], k=1, model=FLXMRglmfix(family="binomial"))

resp <- apply(data.frame(predict(FittedBincat, test[,-which(colnames(test) %in% 'PFI.time')])),1,function(x) which.max(x))

table(test$PFIbucket,resp)
```

```{r model}
repeats = 3
numbers = 10
tunel = 10

set.seed(1234)
x = trainControl(method = 'repeatedcv',
                 number = numbers,
                 repeats = repeats,
                 classProbs = TRUE,
                 summaryFunction = twoClassSummary)

model1 <- train(as.factor(PFIbucket)~. , data = train[,-which(colnames(train) %in% c('PFI.time'))], 
               method = 'knn',
               preProcess = c('center','scale'),
               trControl = x,
               metric = 'ROC',
               tuneLength = tunel)

# Summary of model
model1
plot(model1)


#knncat <- knn(scale(train[,-which(colnames(train) %in% c('PFI.time', 'PFIbucket'))], center = TRUE, scale = TRUE), 
#              test[,-which(colnames(test) %in% c('PFI.time', 'PFIbucket'))],
#              cl = train$PFIbucket,
#              k = 25 )


#table(test$PFIbucket,knncat)
#sum(test$PFIbucket==knncat)/length(test$PFIbucket)
```


```{r model}

rforest <- randomForest(as.factor(PFIbucket) ~ .,  data = train[, -which(names(train) %in% c('PFI.time'))], mtry=3, ntree=1000, importance = TRUE)

resp <- predict(rforest, test[,-which(colnames(test) %in% c('PFI.time','PFIbucket'))])

table(train$PFIbucket,predict(rforest,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))
sum(train$PFIbucket==predict(rforest,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))/length(train$PFIbucket)

table(test$PFIbucket,resp)
sum(test$PFIbucket==resp)/length(test$PFIbucket)
```

```{r}
rforest$importance
varImpPlot(rforest)

```


```{r model}
svmbucket <- svm(as.factor(PFIbucket) ~ .,
               data = train[, -which(names(train) %in% c('PFI.time'))],
               kernel = 'radial')

resp <- predict(svmbucket, test[,-which(colnames(test) %in% c('PFI.time','PFIbucket'))])

table(train$PFIbucket,predict(svmbucket,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))
sum(train$PFIbucket==predict(svmbucket,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))/length(train$PFIbucket)

table(test$PFIbucket,resp)
sum(test$PFIbucket==resp)/length(test$PFIbucket)
```

```{r}

check_dat <- final_sel

check_dat$PFIbucket <- as.factor(ifelse(check_dat$PFI.time<575,1,ifelse(check_dat$PFI.time<1450,2,3)))
```

```{r}
trctrl <- trainControl(method = "repeatedcv", number = 50, repeats = 20)

grid_radial <- expand.grid(scale = c(0.0031, 0.0033,0.0035),
                           C = 1, degree=3)

svm_poly <- train(as.factor(PFIbucket) ~.,
                    data = check_dat[, -which(names(final_sel) %in% c('PFI.time'))],
                    method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_radial,
                    tuneLength = 10)

svm_poly

#svm_pred_poly <- predict(svm_poly, test[, -which(names(test) %in% c('PFI.time','PFIbucket'))])
#confusionMatrix(svm_pred_poly, as.factor(test$PFIbucket))
confusionMatrix(predict(svm_poly, check_dat[, -which(names(check_dat) %in% c('PFIbucket'))]), as.factor(check_dat$PFIbucket))
```


```{r}
write.csv(varImp(svm_poly)$importance, 'svmp2.csv')
```

```{r}
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_radial <- expand.grid(sigma = c( 0.08),
                           C = c(1))

svm_rad <- train(as.factor(PFIbucket) ~.,
                    data = train[, -which(names(train) %in% c('PFI.time'))], 
                    method = "svmRadial",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_radial,
                    tuneLength = 10)

svm_rad

svm_pred_rad <- predict(svm_rad, test[, -which(names(test) %in% c('PFI.time','PFIbucket'))])
confusionMatrix(svm_pred_rad, as.factor(test$PFIbucket))

```
#[,-which(colnames(train) %in% c('PFI.time'))]

```{r}
imp <-varImp(svm_rad)$importance
plot(imp)
print(imp)

write.csv(imp,'svmf.csv')

```


```{r}
start_time <- Sys.time()
  control <- trainControl(method='repeatedcv', 
                          number=8, 
                          repeats=5,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFIbucket) ~.,
                     data =check_dat[, -which(names(check_dat) %in% c('PFI.time'))],
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit


#rf_pred <- predict(rf_fit, check_dat[, -which(names(check_dat) %in% c('PFIbucket'))])
#confusionMatrix(rf_pred, as.factor(check_dat$PFIbucket))
end_time <- Sys.time()

(end_time - start_time)

```


```{r}
model = randomForest(PFIbucket ~.,
                     data =train[, -which(names(train) %in% c('PFI.time'))],mtry =3)
pred = predict(model,train[, -which(names(test) %in% c('PFI.time','PFIbucket'))])
confusionMatrix(pred, as.factor(train$PFIbucket))
```


```{r}
write.csv(varImp(rf_fit)$importance,'randomf2.csv')

```

#https://datascience.stackexchange.com/questions/6838/when-to-use-random-forest-over-svm-and-vice-versa

```{r model}
xgb <- svm(as.factor(PFIbucket) ~ .,
               data = train[,-which(colnames(train) %in% c('PFI.time'))],
               kernel = 'linear')

resp <- predict(svmbucket, test[,-which(colnames(test) %in% c('PFI.time','PFIbucket'))])

table(train$PFIbucket,predict(svmbucket,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))
sum(train$PFIbucket==predict(svmbucket,train[,-which(colnames(train) %in% c('PFI.time','PFIbucket'))]))/length(train$PFIbucket)

table(test$PFIbucket,resp)
sum(test$PFIbucket==resp)/length(test$PFIbucket)
```


```{r}
write.csv(cbind(data.frame(train_dat$participant), predict(FittedBin@models$`3`, train)$Comp.1,predict(FittedBin@models$`3`, train)$Comp.2,predict(FittedBin@models$`3`, train)$Comp.3, clusters(FittedBin@models$`3`,train)), 'cluster_output.csv')

```



```{r}
data1 <- cbind(test[,-which(names(test) %in% c('PFI.time'))], 'PFI.time' = as.integer(predicted$Comp.1))
data2 <- cbind(test[,-which(names(test) %in% c('PFI.time'))], 'PFI.time' = as.integer(predicted$Comp.2))
data3 <- cbind(test[,-which(names(test) %in% c('PFI.time'))], 'PFI.time' = as.integer(predicted$Comp.3))
clust1 <- clusters(FittedBin@models$`3`, newdata = data1)
clust2 <- clusters(FittedBin@models$`3`, newdata = data2)
clust3 <- clusters(FittedBin@models$`3`, newdata = data3)
cbind(clust1,clust2,clust3,'actual'=clusters(FittedBin@models$`3`, newdata = test))

```


```{r}
predictedtrain = predict(FittedBin@models$`4`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`4`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`4`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`4`,train)==2,predictedtrain$Comp.2,ifelse(clusters(FittedBin@models$`4`,train)==3,predictedtrain$Comp.3,predictedtrain$Comp.4)))

ytest2 = ifelse(clusters(FittedBin@models$`4`,test)==1,predicted$Comp.1,ifelse(clusters(FittedBin@models$`4`,test)==2,predicted$Comp.2,ifelse(clusters(FittedBin@models$`4`,test)==3,predicted$Comp.3,predicted$Comp.4)))

sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```

```{r}
predictedtrain = predict(FittedBin@models$`5`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`5`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`5`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`5`,train)==2,predictedtrain$Comp.2,ifelse(clusters(FittedBin@models$`5`,train)==3,predictedtrain$Comp.3,ifelse(clusters(FittedBin@models$`5`,train)==4,predictedtrain$Comp.4,predictedtrain$Comp.5))))

ytest2 = ifelse(clusters(FittedBin@models$`5`,test)==1,predicted$Comp.1,ifelse(clusters(FittedBin@models$`5`,test)==2,predicted$Comp.2,ifelse(clusters(FittedBin@models$`5`,test)==3,predicted$Comp.3,ifelse(clusters(FittedBin@models$`5`,test)==4,predicted$Comp.4,predicted$Comp.5))))

table(clusters(FittedBin@models$`5`,train))
sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```


```{r}
predictedtrain = predict(FittedBin@models$`6`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`6`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`6`,train)==1,predictedtrain$Comp.1,
                 ifelse(clusters(FittedBin@models$`6`,train)==2,predictedtrain$Comp.2,
                        ifelse(clusters(FittedBin@models$`6`,train)==3,predictedtrain$Comp.3,
                               ifelse(clusters(FittedBin@models$`6`,train)==4,predictedtrain$Comp.4,
                                  ifelse(clusters(FittedBin@models$`6`,train)==5,predictedtrain$Comp.5,
                                       predictedtrain$Comp.6)))))

ytest2 = ifelse(clusters(FittedBin@models$`6`,test)==1,predicted$Comp.1,
                ifelse(clusters(FittedBin@models$`6`,test)==2,predicted$Comp.2,
                       ifelse(clusters(FittedBin@models$`6`,test)==3,predicted$Comp.3,
                              ifelse(clusters(FittedBin@models$`6`,test)==4,predicted$Comp.4,
                                ifelse(clusters(FittedBin@models$`6`,test)==5,predicted$Comp.5,predicted$Comp.6)))))
table(clusters(FittedBin@models$`6`,train))
sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```


```{r}
predictedtrain = predict(FittedBin@models$`7`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`7`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`7`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`7`,train)==2,predictedtrain$Comp.2,ifelse(clusters(FittedBin@models$`7`,train)==3,predictedtrain$Comp.3,ifelse(clusters(FittedBin@models$`7`,train)==4,predictedtrain$Comp.4,ifelse(clusters(FittedBin@models$`7`,train)==5,predictedtrain$Comp.5,ifelse(clusters(FittedBin@models$`7`,train)==6,predictedtrain$Comp.6,predictedtrain$Comp.7))))))

ytest2 = ifelse(clusters(FittedBin@models$`7`,test)==1,predicted$Comp.1,
                ifelse(clusters(FittedBin@models$`7`,test)==2,predicted$Comp.2,
                       ifelse(clusters(FittedBin@models$`7`,test)==3,predicted$Comp.3,
                              ifelse(clusters(FittedBin@models$`7`,test)==4,predicted$Comp.4,
                                ifelse(clusters(FittedBin@models$`7`,test)==5,predicted$Comp.5,
                                       ifelse(clusters(FittedBin@models$`7`,test)==6,predicted$Comp.6,predicted$Comp.7))))))
table(clusters(FittedBin@models$`7`,train))
sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```

```{r}
predictedtrain = predict(FittedBin@models$`8`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`8`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`8`,train)==1,predictedtrain$Comp.1,
                 ifelse(clusters(FittedBin@models$`8`,train)==2,predictedtrain$Comp.2,
                        ifelse(clusters(FittedBin@models$`8`,train)==3,predictedtrain$Comp.3,
                               ifelse(clusters(FittedBin@models$`8`,train)==4,predictedtrain$Comp.4,
                                ifelse(clusters(FittedBin@models$`8`,train)==5,predictedtrain$Comp.5,
                                  ifelse(clusters(FittedBin@models$`8`,train)==6, predictedtrain$Comp.6,
                                        ifelse(clusters(FittedBin@models$`8`,train)==7, predictedtrain$Comp.7, predictedtrain$Comp.8)))))))

ytest2 = ifelse(clusters(FittedBin@models$`8`,test)==1,predicted$Comp.1,
                ifelse(clusters(FittedBin@models$`8`,test)==2,predicted$Comp.2,
                       ifelse(clusters(FittedBin@models$`8`,test)==3,predicted$Comp.3,
                              ifelse(clusters(FittedBin@models$`8`,test)==4,predicted$Comp.4,
                                ifelse(clusters(FittedBin@models$`8`,test)==5,predicted$Comp.5,
                                       ifelse(clusters(FittedBin@models$`8`,test)==6,predicted$Comp.6,
                                        ifelse(clusters(FittedBin@models$`8`,test)==7,predicted$Comp.7,predicted$Comp.8)))))))

table(clusters(FittedBin@models$`8`,train))

sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```


## Fitting model on the train data

```{r model}
#mod_fm_train <- flexmix(cbind(as.factor(train$PFI),as.factor(1-train$PFI)) ~ PC1+ 	PC2+ 	PC3+ 	PC4+ 	PC5+ 	PC6+ 
#                                               PC7+ 	PC8+ 	PC9+ 	PC10+ 	PC11+ 	PC12+ 
#                                               PC13+ 	PC14+ 	PC15+ 	PC16+ 	PC17+ 	PC18+ 
#                                               PC19+ 	PC20+ 	Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ 
#                                               Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+ 	                                                         Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=3, model=FLXMRglmfix(family="binomial"))

mod_fm_train <- flexmix((PFI.time) ~ X1+ X2+ X3+ X4+ X5+X6+X7+X8+X9+X0 + Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+  Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=3, model=FLXMRglmfix(family="Gamma"))


check_train <- predict(mod_fm_train)
clust_train <- clusters(mod_fm_train)

#ypredtrain = cbind(check_train$Comp.1, check_train$Comp.2, check_train$Comp.3, check_train$Comp.4, check_train$Comp.5, clust_train)

ypredtrain = cbind((unlist(check_train$Comp.1)), (unlist(check_train$Comp.2)), (unlist(check_train$Comp.3)), clust_train)
ypred = ifelse(ypredtrain[,4]==1, ypredtrain[,1], ifelse(ypredtrain[,4]==2, ypredtrain[,2],ypredtrain[,3]))

#ypred = ifelse(ypredtrain[,6]==1, ypredtrain[,1], ifelse(ypredtrain[,6]==2, ypredtrain[,2],
#                                                         ifelse(ypredtrain[,6]==3, ypredtrain[,3],
#                                                                ifelse(ypredtrain[,6]==4, ypredtrain[,4], ypredtrain[,5]))))

train_rmse = sqrt(mean((ypred-train$PFI.time)^2))
```


## Testing fit on the test data

```{r test fit}
check_test= predict(mod_fm_train, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test = clusters(mod_fm_train, newdata =test)
#ypredtest = cbind(check_test$Comp.1, check_test$Comp.2, check_test$Comp.3,check_test$Comp.4,check_test$Comp.5,clust_test)
#ytest = ifelse(ypredtest[,6]==1, ypredtest[,1], ifelse(ypredtest[,6]==2, ypredtest[,2],
#                                                         ifelse(ypredtest[,6]==3, ypredtest[,3],
#                                                                ifelse(ypredtest[,6]==4, ypredtest[,4], ypredtest[,5]))))

ypredtest = cbind((check_test$Comp.1), (check_test$Comp.2), (check_test$Comp.3), clust_test)
ytest = ifelse(ypredtest[,4]==1, ypredtest[,1], ifelse(ypredtest[,4]==2, ypredtest[,2],ypredtest[,3]))

test_rmse = sqrt(mean((ytest-test$PFI.time)^2))
```


## Model outputs

```{r }
print("RMSE")
cbind(train = train_rmse, test = test_rmse)
print("----------------------------------------------")
rbind(train = table(clust_train), test = table(clust_test))
print("----------------------------------------------")
print("BIC")
BIC(mod_fm_train)
print("----------------------------------------------")
print("AIC")
AIC(mod_fm_train)
```


## Fitting model on the train data (K=4)

```{r model}
mod_fm_train4 <- flexmix((PFI.time) ~ X1+ X2+ X3+ X4+ X5+X6+X7+X8+X9+X0 + Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+  Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=4, model=FLXMRglmfix(family="gaussian"))


check_train4 <- predict(mod_fm_train4)
clust_train4 <- clusters(mod_fm_train4)

ypredtrain4 = cbind((unlist(check_train4$Comp.1)), (unlist(check_train4$Comp.2)), (unlist(check_train4$Comp.3)), (unlist(check_train4$Comp.4)), clust_train4)
ypred4 = ifelse(ypredtrain4[,5]==1, ypredtrain4[,1], ifelse(ypredtrain4[,5]==2, ypredtrain4[,2],
                                                           ifelse(ypredtrain4[,5]==3, ypredtrain4[,3],ypredtrain4[,4])))

train_rmse = sqrt(mean((ypred4-train$PFI.time)^2))
```


## Testing fit on the test data

```{r test fit}
check_test4= predict(mod_fm_train4, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test4 = clusters(mod_fm_train4, newdata =test)

ypredtest = cbind((check_test4$Comp.1), (check_test4$Comp.2), (check_test4$Comp.3),(check_test4$Comp.4), clust_test)
ytest = ifelse(ypredtest[,5]==1, ypredtest[,1], ifelse(ypredtest[,5]==2, ypredtest[,2],
                                                       ifelse(ypredtest[,5]==3, ypredtest[,3],ypredtest[,4])))

test_rmse = sqrt(mean((ytest-test$PFI.time)^2))
```


```{r}
write.csv(cbind(round(ytest,0), test$PFI.time),'resultcomp.csv')
check_test
```

## Model outputs

```{r }
print("RMSE")
cbind(train = train_rmse, test = test_rmse)
print("----------------------------------------------")
rbind(train = table(clust_train4), test = table(clust_test4))
print("----------------------------------------------")
print("BIC")
BIC(mod_fm_train4)
print("----------------------------------------------")
print("AIC")
AIC(mod_fm_train4)
```


## Model Parameters

```{r model parameters}
parameters(mod_fm_train)

par_fm_train = refit(mod_fm_train)
summary(par_fm_train)
```

## Plots of model fit

```{r plots}
  plot(train$ENSG00000139618.13, train$PFI.time, col = c("red","blue","green", "yellow", "black")[clusters(FittedBin@models$`3`,train)],pch = 16,ylab = "PFI.time")

library("ggplot2")
qplot(train$PFI.time, ypred2,xlab="Actual",ylab="Predicted") + geom_abline()
qplot(test$PFI.time, ytest2,xlab="Actual",ylab="Predicted") + geom_abline()

qplot(ypred, ypred2 - train$PFI.time, xlab="Actual Y",ylab="Residual")
qplot(ytest, ytest2 - test$PFI.time, xlab="Actual Y",ylab="Residual")

hist(train$DSS.time[clust_train==1], col = hcl(0, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))
hist(train$DSS.time[clust_train==2], col = hcl(240, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))
hist(train$DSS.time[clust_train==3], col = hcl(135, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))

ys = seq(0, 3500, by = 0.1)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==1]), sd = sd(train$DSS.time[clust_train==1])), col = hcl(0, 80, 50), lwd = 2)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==2]), sd = sd(train$DSS.time[clust_train==2])), col = hcl(240, 80, 50), lwd = 2)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==3]), sd = sd(train$DSS.time[clust_train==3])), col = hcl(135, 80, 50), lwd = 2)

```

# Taking the selected model and building cluster prediction model:
```{r}
selected_model = FittedBin@models$`3`

clust = clusters(selected_model)

```
# Random forest model for cluster prediction

```{r}
library(rpart)
library(rpart.plot)
```

```{r}

rf_class = rpart(as.factor(clust)~.,cbind(train[,-which(colnames(train) %in% 'PFI.time')]))
rpart.plot(rf_class)

```

#testing accuracy

```{r}
t_pred = predict(rf_class,train,type="class")
table(t_pred, clust)

test_pred = predict(rf_class,test,type="class")
table(test_pred, clusters(selected_model, newdata = test))

printcp(rf_class)
```

```{r}
library(randomForest)
rf_class = randomForest(as.factor(clust)~.,cbind(train[1:5]), ntree=50)
plot(rf_class)


```

```{r}

t_pred = predict(rf_class,train,type="class")
table(t_pred, clust)

test_rf = predict(rf_class,test,type="class")
table(test_rf, clusters(selected_model, newdata = test))

```

```{r}
importance(rf_class)
```

```{r}

mylogit <- multinom(as.factor(clust) ~ ., data = cbind(train[, -which(names(test) %in% c('PFI.time'))]))
glm_pred = predict(mylogit,train,type="probs")

cbind(glm_pred, clust)

```
Fitting XGBoost to find clusters



```{r}
library(xgboost)
```


```{r}
train_dat = as.data.frame(cbind(train[1:20], "cluster" = as.factor(clusters(FittedBin@models$`3`,train))))

test_dat = as.data.frame(cbind(test[1:20], "cluster" = as.factor(clusters(FittedBin@models$`3`,test))))
```

```{r}
trainTask <- makeClassifTask(data = train_dat,target = "cluster")


testTask <- makeClassifTask(data = test_dat, target = "cluster")
```


```{r}
set.seed(1)
# Create an xgboost learner that is classification based and outputs
# labels (as opposed to probabilities)
xgb_learner <- makeLearner(
  "classif.xgboost",
  predict.type = "prob",
  par.vals = list(
    objective = "multi:softprob",
    eval_metric = "merror",
    nrounds = 200
  )
)

# Create a model
xgb_model <- train(xgb_learner, task = trainTask)


```

```{r}
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)

```
#Hyper-parameter Tuning

```{r}
# To see all the parameters of the xgboost classifier
getParamSet("classif.xgboost")

```

```{r}
xgb_params <- makeParamSet(
  # The number of trees in the model (each one built sequentially)
  makeIntegerParam("nrounds", lower = 10, upper = 500),
  # number of splits in each tree
  makeIntegerParam("max_depth", lower = 1, upper = 20),
  # "shrinkage" - prevents overfitting
  makeNumericParam("eta", lower = .001, upper = .5),
  # L2 regularization - prevents overfitting
  makeNumericParam("lambda", lower = -1, upper = 0, trafo = function(x) 10^x)
)

control <- makeTuneControlRandom(maxit = 10)

# Create a description of the resampling plan
resample_desc <- makeResampleDesc("CV", iters = 5)

```


```{r}
tuned_params <- tuneParams(
  learner = xgb_learner,
  task = trainTask,
  resampling = resample_desc,
  par.set = xgb_params,
  control = control
)

```



```{r}
# Create a new model using tuned hyperparameters
xgb_tuned_learner <- setHyperPars(
  learner = xgb_learner,
  par.vals = tuned_params$x
)

# Re-train parameters using tuned hyperparameters (and full training set)
xgb_model <- train(xgb_tuned_learner, trainTask)

# Make a new prediction
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)
```


```{r}
ytest = ifelse(result$data$response==1,predicted$Comp.1,
               ifelse(result$data$response==2,predicted$Comp.2,predicted$Comp.3))
#       +result$data$prob.4*predicted$Comp.8+
#        result$data$prob.5*predicted$Comp.5+result$data$prob.6*predicted$Comp.8+
#        result$data$prob.7*predicted$Comp.7+result$data$prob.8*predicted$Comp.8
  

sqrt(mean((test$PFI.time-ytest)^2))
sqrt(mean((test$PFI.time-ytest2)^2))
plot(test$PFI.time,test$PFI.time- ytest)
plot(test$PFI.time, ytest2)

aggregate(cbind(ytest, 'PFI.time'=test$PFI.time, 'clust'=clusters(FittedBin@models$`3`,test)), by=list(clusters(FittedBin@models$`3`,test)), mean )

aggregate(cbind(ypred2, 'PFI.time'=test$PFI.time, 'clust'=clusters(FittedBin@models$`3`,test)), by=list(clusters(FittedBin@models$`3`,test)), mean )

```

```{r}
train_clus = cbind(train, "cluster" = clusters(FittedBin@models$`3`,train))

centers = aggregate(.~cluster,train_clus, FUN = mean)
centers = centers[,2:21]
```


```{r}
distc = data.frame(matrix(NA, nrow(train), 1))
a = list()
for (i in 1:nrow(train)){
  for (j in 1:3){
    a[j] <- as.numeric(dist(rbind(train[i,1:20], centers[j,]),method = "euclidean"))
  }
    
   distc[i,1] <- which.min(unlist(a))
}

colnames(distc) = c('cluster')
head(distc)
```



```{r}
table(distc$cluster, clusters(FittedBin@models$`3`,train))
```

```{r}
library(class)
train_clus = cbind(train[,-which(colnames(train) %in% c('PFI.time'))], 'cluster' = clusters(selected_model,train))
test_clus = cbind(test[,-which(colnames(test) %in% c('PFI.time'))], 'cluster' = clusters(selected_model,test))

test_pred <- knn(train = train_clus, test = test_clus,cl= train_clus$cluster, k = 18)

```

```{r}
install.packages("gmodels")
require("gmodels")
library("gmodels")

CrossTable(x = test_clus$cluster, y = test_pred,
prop.chisq = FALSE)

cbind('xgb'=result$data$response, 'knn' = test_pred, 'rf' = test_rf, 'actual' = test_clus$cluster)
```


# Cluster classification using RNA raw data

```{r}
train_dat = train[,-which(colnames(train) %in% 'PFI.time')]

test_dat = test[, -which(colnames(test) %in% 'PFI.time')]
```

```{r}
trainTask <- makeClassifTask(data = train_dat,target = "PFIbucket")


testTask <- makeClassifTask(data = test_dat, target = "PFIbucket")
```


```{r}
set.seed(1)
# Create an xgboost learner that is classification based and outputs
# labels (as opposed to probabilities)
xgb_learner <- makeLearner(
  "classif.xgboost",
  predict.type = "prob",
  par.vals = list(
    objective = "multi:softprob",
    eval_metric = "merror",
    nrounds = 200
  )
)

# Create a model
xgb_model <- train(xgb_learner, task = trainTask)

```

```{r}
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)

```
#Hyper-parameter Tuning

```{r}
# To see all the parameters of the xgboost classifier
getParamSet("classif.xgboost")

```

```{r}
xgb_params <- makeParamSet(
  # The number of trees in the model (each one built sequentially)
  makeIntegerParam("nrounds", lower = 10, upper = 500),
  # number of splits in each tree
  makeIntegerParam("max_depth", lower = 1, upper = 20),
  # "shrinkage" - prevents overfitting
  makeNumericParam("eta", lower = .001, upper = .5),
  # L2 regularization - prevents overfitting
  makeNumericParam("lambda", lower = -1, upper = 0, trafo = function(x) 10^x)
)

control <- makeTuneControlRandom(maxit = 10)

# Create a description of the resampling plan
resample_desc <- makeResampleDesc("CV", iters = 5)

```


```{r}
tuned_params <- tuneParams(
  learner = xgb_learner,
  task = trainTask,
  resampling = resample_desc,
  par.set = xgb_params,
  control = control
)

```



```{r}
# Create a new model using tuned hyperparameters
xgb_tuned_learner <- setHyperPars(
  learner = xgb_learner,
  par.vals = tuned_params$x
)

# Re-train parameters using tuned hyperparameters (and full training set)
xgb_model <- train(xgb_tuned_learner, trainTask)

# Make a new prediction
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)
```
