---
title: "Flexmix"
author: "Garima Sood"
date: "August 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
library("flexmix")
library(nnet)
library(mlr) 

```

```{r}
install.packages("xgboost")

```

## Load test and train

```{r load data}
train_dat <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/PCA/mol_PCA_train.csv')
head(train_dat)

test_dat <- read.csv('C:/Users/garim/Documents/Capstone/Full data/Normalized/PCA/mol_PCA_test.csv')
head(test_dat)
```
## Fitting flexmix on the molecular data to identify clusters

```{r}
train_sub = train_dat[,c(2:21,109:122)]
pred_subt = flexmix(PFI.time~., data = train_sub, k=3,model = FLXMRglm(family="gaussian"))
clust = clusters(pred_subt)
```




## Subsetting test and train data based on desired variables

```{r subset data}
train  = train_dat[,c(2:21,109:122)]
test  = test_dat[,c(2:21,109:122)]

#train = train[,-which(names(train) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI'))]
#test = test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI'))]

```


## Fitting a step model on the train data

```{r model}
FittedBin <- initFlexmix(PFI.time ~ ., data = train, k=1:5,  nrep =10, model = FLXMRglm(.~.,family="gaussian"))

FittedBin
```

```{r}
linmod = lm(PFI.time ~ ., data = train)
linmod$coefficients
summary(linmod)
```


```{r}
predictedtrain = predict(FittedBin@models$`1`,train[,-which(names(test) %in% c('PFI.time'))])

predicted = predict(FittedBin@models$`1`,test[,-which(names(test) %in% c('PFI.time'))])

ypred2 = predictedtrain$Comp.1
ytest2 = predicted$Comp.1
sqrt(mean((train$PFI.time-ypred2)^2))
sqrt(mean((test$PFI.time-ytest2)^2))
```

```{r}
summary(refit(FittedBin@models$`1`))

```


```{r}
predictedtrain = predict(FittedBin@models$`2`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`2`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])
clusters(FittedBin@models$`2`,test)
ypred2 =  ifelse(clusters(FittedBin@models$`2`,train)==1,predictedtrain$Comp.1,predictedtrain$Comp.2)
ytest2 = ifelse(clusters(FittedBin@models$`2`,test)==1,predicted$Comp.1,predicted$Comp.2)
sqrt(mean((test$PFI.time-ytest2)^2))
sqrt(mean((train$PFI.time-ypred2)^2))
```

```{r}
predictedtrain = predict(FittedBin@models$`3`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`3`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])
table(clusters(FittedBin@models$`3`,train))
ytest2 =  ifelse(clusters(FittedBin@models$`3`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`3`,train)==2,predictedtrain$Comp.2,predictedtrain$Comp.3))
ypred2 = ifelse(clusters(FittedBin@models$`3`,test)==1,predicted$Comp.1,ifelse(clusters(FittedBin@models$`3`,test)==2,
                 predicted$Comp.2,predicted$Comp.3))
sqrt(mean((test$PFI.time-ypred2)^2))
sqrt(mean((train$PFI.time-ytest2)^2))
```

```{r}
cbind(test$PFI.time,ypred2)
```



```{r}
predictedtrain = predict(FittedBin@models$`4`,train[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

predicted = predict(FittedBin@models$`4`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ypred2 =  ifelse(clusters(FittedBin@models$`4`,train)==1,predictedtrain$Comp.1,ifelse(clusters(FittedBin@models$`4`,train)==2,predictedtrain$Comp.2,ifelse(clusters(FittedBin@models$`4`,train)==3,predictedtrain$Comp.3,predictedtrain$Comp.4)))

ytest2 = ifelse(clusters(FittedBin@models$`4`,test)==1,predicted$Comp.1,ifelse(clusters(FittedBin@models$`4`,test)==2,predicted$Comp.2,ifelse(clusters(FittedBin@models$`4`,test)==3,predicted$Comp.3,predicted$Comp.4)))

sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))



```

## Fitting model on the train data

```{r model}
#mod_fm_train <- flexmix(cbind(as.factor(train$PFI),as.factor(1-train$PFI)) ~ PC1+ 	PC2+ 	PC3+ 	PC4+ 	PC5+ 	PC6+ 
#                                               PC7+ 	PC8+ 	PC9+ 	PC10+ 	PC11+ 	PC12+ 
#                                               PC13+ 	PC14+ 	PC15+ 	PC16+ 	PC17+ 	PC18+ 
#                                               PC19+ 	PC20+ 	Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ 
#                                               Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+ 	                                                         Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=3, model=FLXMRglmfix(family="binomial"))

mod_fm_train <- flexmix((PFI.time) ~ X1+ X2+ X3+ X4+ X5+X6+X7+X8+X9+X0 + Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+  Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=3, model=FLXMRglmfix(family="Gamma"))


check_train <- predict(mod_fm_train)
clust_train <- clusters(mod_fm_train)

#ypredtrain = cbind(check_train$Comp.1, check_train$Comp.2, check_train$Comp.3, check_train$Comp.4, check_train$Comp.5, clust_train)

ypredtrain = cbind((unlist(check_train$Comp.1)), (unlist(check_train$Comp.2)), (unlist(check_train$Comp.3)), clust_train)
ypred = ifelse(ypredtrain[,4]==1, ypredtrain[,1], ifelse(ypredtrain[,4]==2, ypredtrain[,2],ypredtrain[,3]))

#ypred = ifelse(ypredtrain[,6]==1, ypredtrain[,1], ifelse(ypredtrain[,6]==2, ypredtrain[,2],
#                                                         ifelse(ypredtrain[,6]==3, ypredtrain[,3],
#                                                                ifelse(ypredtrain[,6]==4, ypredtrain[,4], ypredtrain[,5]))))

train_rmse = sqrt(mean((ypred-train$PFI.time)^2))
```


## Testing fit on the test data

```{r test fit}
check_test= predict(mod_fm_train, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test = clusters(mod_fm_train, newdata =test)
#ypredtest = cbind(check_test$Comp.1, check_test$Comp.2, check_test$Comp.3,check_test$Comp.4,check_test$Comp.5,clust_test)
#ytest = ifelse(ypredtest[,6]==1, ypredtest[,1], ifelse(ypredtest[,6]==2, ypredtest[,2],
#                                                         ifelse(ypredtest[,6]==3, ypredtest[,3],
#                                                                ifelse(ypredtest[,6]==4, ypredtest[,4], ypredtest[,5]))))

ypredtest = cbind((check_test$Comp.1), (check_test$Comp.2), (check_test$Comp.3), clust_test)
ytest = ifelse(ypredtest[,4]==1, ypredtest[,1], ifelse(ypredtest[,4]==2, ypredtest[,2],ypredtest[,3]))

test_rmse = sqrt(mean((ytest-test$PFI.time)^2))
```


```{r}
write.csv(cbind(round(ytest,0), test$PFI.time),'resultcomp.csv')
check_test
```

## Model outputs

```{r }
print("RMSE")
cbind(train = train_rmse, test = test_rmse)
print("----------------------------------------------")
rbind(train = table(clust_train), test = table(clust_test))
print("----------------------------------------------")
print("BIC")
BIC(mod_fm_train)
print("----------------------------------------------")
print("AIC")
AIC(mod_fm_train)
```


## Fitting model on the train data (K=4)

```{r model}
mod_fm_train4 <- flexmix((PFI.time) ~ X1+ X2+ X3+ X4+ X5+X6+X7+X8+X9+X0 + Cyclophosphamide+ 	Doxorubicin+ 	Tamoxifen+ 	Anastrozole+ Paclitaxel+ 	Docetaxel+ 	Fluorouracil+ 	Trastuzumab+ 	Letrozole+  Exemestane+ Epirubicin+ 	Carboplatin+ 	Methotrexate, data = train, k=4, model=FLXMRglmfix(family="gaussian"))


check_train4 <- predict(mod_fm_train4)
clust_train4 <- clusters(mod_fm_train4)

ypredtrain4 = cbind((unlist(check_train4$Comp.1)), (unlist(check_train4$Comp.2)), (unlist(check_train4$Comp.3)), (unlist(check_train4$Comp.4)), clust_train4)
ypred4 = ifelse(ypredtrain4[,5]==1, ypredtrain4[,1], ifelse(ypredtrain4[,5]==2, ypredtrain4[,2],
                                                           ifelse(ypredtrain4[,5]==3, ypredtrain4[,3],ypredtrain4[,4])))

train_rmse = sqrt(mean((ypred4-train$PFI.time)^2))
```


## Testing fit on the test data

```{r test fit}
check_test4= predict(mod_fm_train4, newdata = test[, -which(names(test) %in% c('PFI.time'))])
clust_test4 = clusters(mod_fm_train4, newdata =test)

ypredtest = cbind((check_test4$Comp.1), (check_test4$Comp.2), (check_test4$Comp.3),(check_test4$Comp.4), clust_test)
ytest = ifelse(ypredtest[,5]==1, ypredtest[,1], ifelse(ypredtest[,5]==2, ypredtest[,2],
                                                       ifelse(ypredtest[,5]==3, ypredtest[,3],ypredtest[,4])))

test_rmse = sqrt(mean((ytest-test$PFI.time)^2))
```


```{r}
write.csv(cbind(round(ytest,0), test$PFI.time),'resultcomp.csv')
check_test
```

## Model outputs

```{r }
print("RMSE")
cbind(train = train_rmse, test = test_rmse)
print("----------------------------------------------")
rbind(train = table(clust_train4), test = table(clust_test4))
print("----------------------------------------------")
print("BIC")
BIC(mod_fm_train4)
print("----------------------------------------------")
print("AIC")
AIC(mod_fm_train4)
```


## Model Parameters

```{r model parameters}
parameters(mod_fm_train)

par_fm_train = refit(mod_fm_train)
summary(par_fm_train)
```

## Plots of model fit

```{r plots}
plot(train$X0, train$PFI.time, col = c("red","blue","green", "yellow", "black")[clusters(FittedBin@models$`4`,train)],pch = 16,ylab = "PFI.time")

library("ggplot2")
qplot(train$PFI.time, ypred2,xlab="Actual",ylab="Predicted") + geom_abline()
qplot(test$PFI.time, ytest2,xlab="Actual",ylab="Predicted") + geom_abline()

qplot(ypred, ypred2 - train$PFI.time, xlab="Actual Y",ylab="Residual")
qplot(ytest, ytest2 - test$PFI.time, xlab="Actual Y",ylab="Residual")

hist(train$DSS.time[clust_train==1], col = hcl(0, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))
hist(train$DSS.time[clust_train==2], col = hcl(240, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))
hist(train$DSS.time[clust_train==3], col = hcl(135, 50, 80), main = "",xlab = "", freq = FALSE, ylim = c(0,0.001))

ys = seq(0, 3500, by = 0.1)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==1]), sd = sd(train$DSS.time[clust_train==1])), col = hcl(0, 80, 50), lwd = 2)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==2]), sd = sd(train$DSS.time[clust_train==2])), col = hcl(240, 80, 50), lwd = 2)
lines(ys, dnorm(ys, mean = mean(train$DSS.time[clust_train==3]), sd = sd(train$DSS.time[clust_train==3])), col = hcl(135, 80, 50), lwd = 2)

```

# Taking the selected model and building cluster prediction model:
```{r}
selected_model = FittedBin@models$`4`

clust = clusters(selected_model)

```
# Random forest model for cluster prediction

```{r}
library(rpart)
library(rpart.plot)
```

```{r}

rf_class = rpart(as.factor(clust)~.,cbind(train[, -which(names(test) %in% c('PFI.time'))]))
rpart.plot(rf_class)

```

#testing accuracy

```{r}
t_pred = predict(rf_class,train,type="class")
table(t_pred, clust)

test_pred = predict(rf_class,test,type="class")
table(test_pred, clusters(selected_model, newdata = test))

printcp(rf_class)
```

```{r}
predicted = predict(FittedBin@models$`4`,test[,-which(names(test) %in% c('OS','OS.time', 'DSS', 'DSS.time', 'PFI','PFI.time'))])

ytest2 = ifelse(test_pred==1,predicted$Comp.1,ifelse(test_pred==2,predicted$Comp.2,ifelse(test_pred==3,predicted$Comp.3, predicted$Comp.4)))

sqrt(mean((test$PFI.time-ytest2)^2))

sqrt(mean((train$PFI.time-ypred2)^2))


```
```{r}
library("randomForest")
```


```{r}

rf_class = randomForest(as.factor(clust)~.,cbind(train[, -which(names(test) %in% c('PFI.time'))]))
plot(rf_class)



```

```{r}

t_pred = predict(rf_class,train,type="class")
table(t_pred, clust)

test_pred = predict(rf_class,test,type="class")
table(test_pred, clusters(selected_model, newdata = test))

```

```{r}
importance(rf_class)
```

```{r}

mylogit <- multinom(as.factor(clust) ~ ., data = cbind(train[, -which(names(test) %in% c('PFI.time'))]))
glm_pred = predict(mylogit,train,type="probs")
library(rcompanion)

nagelkerke(mylogit)

```
Fitting XGBoost to find clusters



```{r}
library(xgboost)
```


```{r}
train_dat = as.data.frame(cbind(train[, -which(names(train) %in% c('PFI.time'))], "cluster" = as.factor(clusters(FittedBin@models$`2`,train))))

test_dat = as.data.frame(cbind(test[, -which(names(test) %in% c('PFI.time'))], "cluster" = as.factor(clusters(FittedBin@models$`2`,test))))
```

```{r}
trainTask <- makeClassifTask(data = train_dat,target = "cluster")


testTask <- makeClassifTask(data = test_dat, target = "cluster")
```


```{r}
set.seed(1)
# Create an xgboost learner that is classification based and outputs
# labels (as opposed to probabilities)
xgb_learner <- makeLearner(
  "classif.xgboost",
  predict.type = "response",
  par.vals = list(
    objective = "multi:softmax",
    eval_metric = "merror",
    nrounds = 200
  )
)

# Create a model
xgb_model <- train(xgb_learner, task = trainTask)


```

```{r}
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)

```
#Hyper-parameter Tuning

```{r}
# To see all the parameters of the xgboost classifier
getParamSet("classif.xgboost")

```

```{r}
xgb_params <- makeParamSet(
  # The number of trees in the model (each one built sequentially)
  makeIntegerParam("nrounds", lower = 20, upper = 500),
  # number of splits in each tree
  makeIntegerParam("max_depth", lower = 1, upper = 10),
  # "shrinkage" - prevents overfitting
  makeNumericParam("eta", lower = .01, upper = .5),
  # L2 regularization - prevents overfitting
  makeNumericParam("lambda", lower = -1, upper = 0, trafo = function(x) 10^x)
)

control <- makeTuneControlRandom(maxit = 10)

# Create a description of the resampling plan
resample_desc <- makeResampleDesc("CV", iters = 5)

```


```{r}
tuned_params <- tuneParams(
  learner = xgb_learner,
  task = trainTask,
  resampling = resample_desc,
  par.set = xgb_params,
  control = control
)

```



```{r}
# Create a new model using tuned hyperparameters
xgb_tuned_learner <- setHyperPars(
  learner = xgb_learner,
  par.vals = tuned_params$x
)

# Re-train parameters using tuned hyperparameters (and full training set)
xgb_model <- train(xgb_tuned_learner, trainTask)

# Make a new prediction
result <- predict(xgb_model, testTask)
table(result$data$truth,result$data$response)
```


```{r}
ytest = ifelse(result$data$response ==1, predicted$Comp.1,predicted$Comp.2)

sqrt(mean((test$PFI.time-ytest)^2))
sqrt(mean((test$PFI.time-ytest2)^2))
plot(test$PFI.time, ytest)
plot(test$PFI.time, ytest2)

```








