---
title: "Report_implementation"
author: "Samia Feroze"
date: "10/4/2018"
output: html_document
---

#Running regression with PFI time

```{r}
library(classInt)
#install.packages("plotmo")
library(plotmo)
TOP_20<-read.csv("C:/Users/garim/Documents/Capstone/Codes/Flexmix/topvar.csv")
```


```{r}
TOP_20[,c(4,13)] <- lapply(TOP_20[,c(4,13)], as.factor)
classIntervals(TOP_20$PFI.time, 2, style = 'quantile')
TOP_20$PFI_2_bucket <- as.factor(ifelse(TOP_20$PFI.time<776,1,2))
write.csv(TOP_20 ,"top_20.csv")
TOP_20_time<-TOP_20[-c(2,27)]
```

```{r}
#smp_size<-floor(0.75*nrow(TOP_20))
#set.seed(123)
#train_ind <- sample(seq_len(nrow(TOP_20)), size = smp_size)
#train <- TOP_20[train_ind , ]
#test<- TOP_20[-train_ind, ] 
```

```{r}
library(leaps)

TOP_20_time$PFI.time.sqrt<-sqrt(TOP_20_time$PFI.time)

Linearregression<-lm(PFI.time.sqrt~., data=TOP_20_time[-c(1)])
summary(Linearregression)
plot(Linearregression$residuals)
plot(TOP_20_time$PFI.time, Linearregression$fitted.values)
```

#Running RF with PFI time

```{r}
library(caret)
control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(PFI.time ~.,
                     data =TOP_20_time,
                     method = 'rf',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  plotres()

```

#Running PFI time with SVR

```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:6)

svm_poly <- train(PFI.time ~.
                    ,data = TOP_20_time[-c(1,26)], method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    tuneLength = 10)

varImp(svm_poly)
plotres(svm_poly)
svm_poly$results
plot(svm_poly)
plot(svm_poly$results[,c("Rsquared")], type="l")
varImp(svm_poly)
```

#Running cross validated linear regression with PFI time

```{r}
library(DAAG)
cvResults <- CVlm(data=TOP_20_time[-c(25)], m=5, form.lm = formula(PFI.time~ .))
plot(cvResults$cvpred,TOP_20_time$PFI.time )
residuals = sum(cvResults$cvpred-TOP_20_time$PFI.time)

# performs the CV
```

#Running regression with PFI time square rooted

```{r}
library(DAAG)
cvResults_sqrt <- CVlm(data=TOP_20_time[-c(1,2)], m=5, form.lm = formula(PFI.time.sqrt ~ .))
plot(cvResults$cvpred,TOP_20_time$PFI.time.sqrt )
plotres(cvResults_sqrt)

```



```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:6)

svm_poly <- train(PFI.time.sqrt ~.
                    ,data = TOP_20_time[-c(1)], method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    tuneLength = 10)

varImp(svm_poly)

svm_poly$results
plot(svm_poly)
plot(svm_poly$results[,c("Rsquared")], type="l")
varImp(svm_poly)

```


#Running rf fit with pfi time 
```{r}
library(caret)
control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid', savePredictions = T)
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train (PFI.time.sqrt ~.,
                     data =TOP_20_time[-c(1,2)],
                     method = 'rf',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  res<-rf_fit$pred
  
  rf_fit
  plot(rf_fit)
  plotres(rf_fit)
```


#Fitting rf model with 3 classes and only genes

```{r}
#colnames(train)
train_genes<-TOP_20[-c(1,3,4,13:27)]
test_genes<-TOP_20[-c(1,3,4,13:27)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFIbucket) ~.,
                     data =train_genes,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  plot(rf_fit)
```

#Fitting rf model with 3 classes only drugs

```{r}
train_drugs<-TOP_20[c(2,14:26)]
test_drugs<-TOP_20[c(2,14:26)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit_drugs <- train(as.factor(PFIbucket) ~.,
                     data =train_drugs,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit_drugs
  plot(rf_fit_drugs)
```
```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:6)

svm_poly <- train(PFI.time.sqrt ~.
                    ,data = TOP_20_time[-c(1)], method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    tuneLength = 10)

varImp(svm_poly)

svm_poly$results
plot(svm_poly)
plot(svm_poly$results[,c("Rsquared")], type="l")
varImp(svm_poly)
```



#Fitting rf model with 3 classes and only genes

```{r}
#colnames(train)
train_genes<-TOP_20[-c(1,3,4,13:27)]
test_genes<-TOP_20[-c(1,3,4,13:27)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFIbucket) ~.,
                     data =train_genes,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  plot(rf_fit)
```

#Fitting across 2 classes

```{r}

TOP_20_2c<-TOP_20[-c(1,2,3)]
colnames(TOP_20)

```


#fitting across 2 classes and only genes

```{r}
#colnames(train)
train_genes<-TOP_20_2c[c(2:9,24)]
test_genes<-TOP_20_2c[c(2:9,24)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFI_2_bucket) ~.,
                     data =train_genes,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  plot(rf_fit)
```



#Fitting across 2 classes and only drugs

```{r}
train_drugs<-TOP_20_2c[c(11:24)]
test_drugs<-TOP_20_2c [c(11:24)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit_drugs <- train(as.factor(PFI_2_bucket) ~.,
                     data =train_drugs,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit_drugs
  plot(rf_fit_drugs)
```


```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:6)

svm_poly <- train(PFI_2_bucket ~.
                    ,data = train_drugs, method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    tuneLength = 10)

varImp(svm_poly)

svm_poly$results
plot(svm_poly)
plot(svm_poly$results[,c("Rsquared")], type="l")
varImp(svm_poly)
```

#Fitting logistic regression


```{r}
# Fit the model
model_log <- nnet::multinom(PFI_2_bucket ~., data = TOP_20_2c)
# Summarize the model
summary(model_log)
# Make predictions
```

#Fitting logistic with lasso

```{r}
library(glmnet)
X<- data.matrix(TOP_20_2c[-c(24)])
Y<- data.matrix(TOP_20_2c[c(24)])
glmmod <- glmnet(X, y=as.factor(Y), alpha=1, family="binomial")
plot(glmmod, xvar="lambda")
cv.out=cv.glmnet(x=X,y=Y,alpha=1)
plot(cv.out)

(bestlam =cv.out$lambda.min)
s="bestlam"
lass.train=predict(glmmod, s=bestlam, newx=X, "class")
#lasso.pred=predict(glmmod,s=bestlam,
                   #newx=data.matrix(test_2c[-c(24)]), "class")

print_glmnet_coefs <- function(cv.out, s="bestlam") {
    ind <- which(coef(cv.out, s=s) != 0.0000)
    df <- data.frame(
        feature=rownames(coef(cv.out, s=s))[ind],
        coeficient=coef(cv.out, s=s)[ind]
    )
    kable(df)
}
plot(cv.out$cvm)
confusionMatrix(TOP_20_2c$PFI_2_bucket, as.factor(lass.train))
print_glmnet_coefs(cv.out,s)


train = read.csv("train.csv", stringsAsFactors=FALSE)

train$Age[is.na(train$Age)] = 29.70

formula = PFI_2_bucket ~ .

# use glm() no cross validation
modelLog = glm(formula, data=TOP_20_2c, family=binomial)
PredTrain = predict(modelLog, newdata=train, type="response") 
table(train$Survived, PredTrain > 0.5)

library(caret)

# use caret's glm with cross validation
train_control = trainControl(method="cv", number=5)

modelLog = train (formula, data = TOP_20_3c, method = "glm", family = multinom, trControl = train_control)

PredTrain = predict(modelLog, newdata=TOP_20_2c, type="raw") 

table(TOP_20_2c$PFI_2_bucket, PredTrain)

confusionMatrix(modelLog)


plot(varImp(modelLog))

cv.10.folds <- createFolds(To, k = 10)
lasso_grid <- expand.grid(fraction=c(1,0.1,0.01,0.001))

lasso <- train ( medv ~ ., data = df, 
               preProcess = c("center", "scale"), 
               method ='lasso',
               tuneGrid = lasso_grid,
               trControl= trainControl( method = "cv", number = 10, index = cv.10.folds))  


tuneGrid=expand.grid(alpha=1,lambda=seq(0, 100, by = 0.1))


trainControl <- trainControl(method = "cv",
                       number = 10,
                       # Compute Recall, Precision, F-Measure
                       summaryFunction = prSummary,
                       # prSummary needs calculated class probs
                       classProbs = T, savePredictions = T)

modelFit <- train(as.factor(PFI_2_bucket) ~ . , data = TOP_20_2c, 
            method = "glmnet", 
            trControl = trainControl,
            metric = "Recall",
            family="binomial")

confusionMatrix(modelFit)
plot(modelFit)
ROC(modelFit$pred[selectedIndices, ]$first, modelFit$pred[selectedIndices, ]$obs=="first")
  
```


#Fitting SVM with radial kernel

```{r}
library(caret)
 svm_Radial <- train(PFI_2_bucket ~., data = TOP_20_2c, method = "svmRadial",
  trControl=trctrl,
  preProcess = c("center", "scale"),
  tuneLength = 10)


trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
grid_radial <- expand.grid(sigma = c(0.025, 0.03, 0.037, 0.04,
 0.05, 0.06),
 C = c(0.25, 0.5, 0.75, 1, 1.5, 2,5))

set.seed(3233)
svm_Radial_Grid <- train(PFI_2_bucket ~., data = TOP_20_2c, method = "svmRadial",
                    trControl=control,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_radial,
                    metric = 'Sens',
                    tuneLength = 10)



plot(svm_Radial_Grid)
#ROC
ROC(svm_Radial_Grid$pred[selectedIndices, ]$first, svm_Radial_Grid$pred[selectedIndices, ]$obs=="first")
```

```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:6)

svm_poly <- train(PFI_2_bucket ~.
                    ,data = TOP_20_2c, method = "svmPoly",
                    trControl=control,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    metric =  'Sens',
                    tuneLength = 10)

svm_poly
plot(svm_poly)
confusionMatrix(svm_poly)
write.csv(svm_poly$results, "svm_2_class.csv")
#ROC
ROC(svm_poly$pred[selectedIndices, ]$first, svm_poly$pred[selectedIndices, ]$obs=="first")
```

#RF fit
```{r}
library("plyr")
library("ggplot2")
library(caret)
library(ggplot2)
library(mlbench)
library(plotROC)
library(Epi)
TOP_20_2c$PFI_2_bucket<-mapvalues(TOP_20_2c$PFI_2_bucket, from = c("1", "2"), to = c("first", "second"))
TOP_20_2c$PFI_2_bucket<-NULL

control <- trainControl(method = "repeatedcv",   # 10fold cross validation
                     number = 5,							# do 5 repititions of cv
                     summaryFunction=twoClassSummary,	# Use AUC to pick the best model
                     classProbs=TRUE,
                     allowParallel = TRUE, savePredictions=T)
 
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFI_2_bucket) ~.,
                     data = TOP_20_2c,
                     method = 'rf',
                     metric = 'Sens',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
residualValues.RF <- TOP_20_time$PFI.time.sqrt - rf_fit$pred$pred
  plot(rf_fit$pred, residualValues.RF)
plot(rf_fit$pred$pred, residualValues.RF, ylab = "Residual", xlab = "Predicted values")
abline(h = 0, col = "darkgrey", lty = 2)
plot(rf_fit)
ROC(rf_fit$pred[selectedIndices, ]$first, rf_fit$pred[selectedIndices, ]$obs=="first")
confusionMatrix(rf_fit)
  
  


  rf_fit$pred$mtry==2
  selectedIndices <- rf_fit$pred$mtry == 2
  g <- ggplot(rf_fit$pred[selectedIndices, ]$pred, aes(m=second, d=factor(obs, levels = c("first", "second")))) + 
  geom_roc(n.cuts=0) + 
  coord_equal() +
  style_roc()

g + annotate("text", x=0.75, y=0.25, label=paste("AUC =", round((calc_auc(g))$AUC, 4)))
  #print(rf_fit)
  #plot(rf_fit)

  ctrl = trainControl(method="repeatedcv", number=10, repeats = 300, savePredictions = TRUE, classProbs = TRUE)
mdl = train("Label~.", data=Data, method = "glm", trControl = ctrl)
pred = predict(mdl, newdata = Data, type="prob")
roc.1 = roc(Data$Label, pred$control)
roc.2 = roc(mdl$pred$obs,mdl$pred$control)
roc.3 = roc(as.numeric(rf_fit$trainingData$.outcome=='case'),aggregate(case~rowIndex,mdl$pred,mean)[,'case'])
```

```{r}
  
  ##roc
  
  library(pROC)
#probsTrain <- predict(tune, train, type = "prob")
rocCurve   <- roc(response = (TOP_20_2c$PFI_2_bucket=="second")*1,
                      predictor =rf_fit$pred[selectedIndices, ]$second,
                      levels = rev(levels(TOP_20_2c$PFI_2_bucket))
                  )
plot(rocCurve, print.thres = "best")

ibrary(pROC)
probsTrain <- predict(tune, train, type = "prob")
rocCurve   <- roc(response = train$response,
                      predictor = probsTrain[, "yes"],
                      levels = rev(levels(train$response)))
plot(rocCurve, print.thres = "best")
```



#Fitting across 3 classes


```{r}

TOP_20_3c<-TOP_20[-c(1,3,27)]
colnames(TOP_20_3c)
#TOP_20_3c$dox_cyc <- pmax(TOP_20_3c$Doxorubicin,TOP_20_3c$Cyclophosphamide)
# TOP_20_3c <- TOP_20_3c[,-c(12,13)]
```


#Fitting logistic regression


```{r}
# Fit the model
library(nnet)
model_log <- nnet::multinom(PFIbucket ~., data = TOP_20_3c)
# Summarize the model
summary(model_log)
```

#Fitting logistic with lasso

```{r}
library(knitr)
library("classInt")
X<- data.matrix(TOP_20_3c[-c(1,2)])
Y<- data.matrix(TOP_20_3c[c(2)])
glmmod <- glmnet(X, y=as.factor(Y), alpha=1, family="multinomial")
plot(glmmod, xvar="lambda")
cv.out=cv.glmnet(x=X,y=Y,alpha=1)
plot(cv.out)

(bestlam =cv.out$lambda.min)
s="bestlam"
#lasso.pred=predict(glmmod,s=bestlam,
                   #newx=data.matrix(test_2c[-c(24)]), "class")
lass.train=predict(glmmod, s=bestlam, newx=X, "class")
print_glmnet_coefs <- function(cv.out, s="bestlam") {
    ind <- which(coef(cv.out, s=s) != 0.0000)
    df <- data.frame(
        feature=rownames(coef(cv.out, s=s))[ind],
        coeficient=coef(cv.out, s=s)[ind]
    )
    kable(df)
}
plot(cv.out$cvm)
confusionMatrix(as.factor(Y), as.factor(lass.train))
print_glmnet_coefs(cv.out,cv.out$lambda.min)
```

#Fitting SVM with radial kernel

```{r}
library(caret)

 svm_Radial <- train(PFIbucket ~., data = TOP_20_3c, method = "svmRadial",
  trControl=trctrl,
  preProcess = c("center", "scale"),
  tuneLength = 10)


trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
grid_radial <- expand.grid(sigma = c(0.025, 0.03, 0.037, 0.04,
 0.05, 0.06),
 C = c(0.25, 0.5, 0.75, 1, 1.5, 2,5))
set.seed(3233)
(svm_Radial_Grid <- train(PFIbucket ~., data = TOP_20_3c, method = "svmRadial",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_radial,
                    tuneLength = 10))

confusionMatrix(svm_Radial_Grid)
plot(svm_Radial_Grid)
# Set up the 5-fold CV
#fitControl <- caret::trainControl(method = "cv",number = 5)

# Define ranges for the two parameters
#C_range =     sapply(seq(-1,3,0.0125), function(x) 10^x)
#sigma_range = sapply(seq(-3,1,0.0125), function(x) 10^x)

# Create the grid of parameters
#fitGrid <- expand.grid(C     = C_range,
                       #sigma = sigma_range)

# Set a random seed for reproducibility
#set.seed(825)

# Train the model using our previously defined parameters
#Rsvm <- caret::train(PFIbucket ~ ., data = TOP_20_3c,
                 #method = "svmRadial",
                 #trControl = fitControl,
                 #tuneGrid = fitGrid)

#Rsvm
#plot(Rsvm)
```

#FITTING SVM POLYNOMIAL

```{r}
library(caret)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

grid_poly <- expand.grid(scale = c(0.001,0.0015,0.002,0.003,0.005),
                           C = c(0.5,0.8,0.9,1,1.2,1.4,1.6,2,2.5), degree=1:8)

svm_poly <- train(PFIbucket ~.
                    ,data = TOP_20_3c, method = "svmPoly",
                    trControl=trctrl,
                    preProcess = c("center", "scale"),
                    tuneGrid = grid_poly,
                    tuneLength = 10)

svm_poly
confusionMatrix(svm_poly)
plot(svm_poly)
write.csv(svm_poly$results, "svm_3_class.csv")
```

#RF fit
```{r}

library(caret)
control <- trainControl(method='repeatedcv', 
                          number=10, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:6)
  rf_fit <- train(as.factor(PFIbucket) ~.,
                     data = TOP_20_3c[,-which(colnames(TOP_20_3c_polr_sc) %in% ('Epirubicin'))],
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 10,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  confusionMatrix(rf_fit)
  plot(rf_fit)
  varImp(rf_fit)
  plot(varImp(rf_fit))
  write.csv(varImp(rf_fit)$importance, "varimpt_rf.csv")
```

#Fitting a tree model to understand interactions

```{r}
library(rpart)
library(rpart.plot)

trmod <- rpart(as.factor(PFIbucket) ~., data = TOP_20_3c[,-which(colnames(TOP_20_3c) %in% ('Epirubicin'))])
plotcp(trmod)
printcp(trmod)

prtrmod <- prune(trmod, cp = 0.014 )
rpart.plot(prtrmod)


table(TOP_20_3c$PFIbucket, predict(prtrmod,TOP_20_3c, type = 'class'))

print(prtrmod)
```


```{r}
trctrl <- trainControl(method = "repeatedcv", number = 8, repeats = 5)
dtree_fit <- train(as.factor(PFIbucket) ~., data = TOP_20_3c[,-which(colnames(TOP_20_3c) %in% ('Epirubicin'))], method = "rpart",
                   trControl=trctrl,tuneLength = 10)
library(rpart.plot)
rpart.plot(dtree_fit$finalModel, type=2, cex=0.5, space = 0.5, gap = 0.5,fallen.leaves=TRUE)
#dtree_fit
```


# Fitting a logistic regression model with interaction terms:

```{r}
library(nnet)

data_test <- TOP_20_3c
data_test$dox_stg1 <- data_test$Doxorubicin*(as.numeric(data_test$ajcc_pathologic_tumor_stage.Stage.I)-1)

int_mod <-multinom(as.factor(PFIbucket) ~ 
                                Doxorubicin*ajcc_pathologic_tumor_stage.Stage.I*ENSG00000103269*ENSG00000102796
                              + Doxorubicin*ENSG00000102796*cg02282892*ENSG00000100906
                              + Doxorubicin*ENSG00000102796*cg05337753*ENSG00000198832
                              + ENSG00000134917+
                              + hsa.mir.146a+ajcc_pathologic_tumor_stage.Stage.3+Cyclophosphamide + Tamoxifen
                              + Anastrozole+ Paclitaxel+ Docetaxel +Trastuzumab +Letrozole+  Fluorouracil+
                              + Exemestane+ Carboplatin+ Methotrexate,
         data = TOP_20_3c_polr_sc)
#*ENSG00000103269*ENSG00000102796
```

```{r}
coefficients(int_mod)


```

```{r}
summary((int_mod))

```

Checking p-values of the coefficients:

```{r}
z <- summary(int_mod)$coefficients/summary(int_mod)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2
round(p,2)
```

```{r}
library(MASS)

TOP_20_3c_polr_sc <- data.frame(scale(TOP_20_3c[,-c(1,2,11)], center = TRUE, scale = TRUE))
TOP_20_3c_polr_sc <- data.frame(cbind("PFIbucket"= TOP_20_3c$PFIbucket, 
                           "Tumor_Stage.I"=TOP_20_3c$ajcc_pathologic_tumor_stage.Stage.I,
                           "Tumor_Stage.3"=TOP_20_3c$ajcc_pathologic_tumor_stage.Stage.3,
                           TOP_20_3c_polr_sc))

polr_mod <- polr(PFIbucket ~ 
                                Doxorubicin*Tumor_Stage.I*ENSG00000103269*ENSG00000102796
                              + Doxorubicin*ENSG00000102796*cg02282892*ENSG00000100906
                              + Doxorubicin*ENSG00000102796*cg05337753*ENSG00000198832
                              + ENSG00000134917+ hsa.mir.146a+Tumor_Stage.3
                              + Cyclophosphamide + Tamoxifen
                              + Anastrozole+ Paclitaxel+ Docetaxel +Trastuzumab +Letrozole+  Fluorouracil+
                              + Exemestane+ Carboplatin+ Methotrexate,
         data = TOP_20_3c_polr_sc) 

#summary(polr_mod)
#library(AER) 
coeftest(polr_mod) 
```


Reference for polr understanding: https://data.library.virginia.edu/fitting-and-interpreting-a-proportional-odds-model/
Effects plots: https://cran.r-project.org/web/packages/sjPlot/vignettes/plot_interactions.html

```{r}

library(effects)
(allEffects(polr_mod))

```

```{r}
library(sjPlot)

plot(Effect(focal.predictors = c("ajcc_pathologic_tumor_stage.Stage.I","Doxorubicin"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Doxorubicin"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tumor_Stage.I","Docetaxel"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000103269","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Doxorubicin"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","Docetaxel"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000102796","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000100906","Doxorubicin"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","Docetaxel"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("cg02282892","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Doxorubicin"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg02282892","Docetaxel"), polr_mod), style="stacked")


plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","ENSG00000198832","cg05337753"), polr_mod,xlevels=3), style="stacked")
plot(Effect(focal.predictors = c("Tumor_Stage.I","ENSG00000103269","ENSG00000102796"),polr_mod,xlevels=3), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Doxorubicin"), polr_mod,xlevels=3), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg02282892","Docetaxel"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Anastrozole"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Doxorubicin"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Trastuzumab"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Tamoxifen"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Paclitaxel"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000102796","cg05337753","Docetaxel"), polr_mod), style="stacked")



plot(Effect(focal.predictors = c("ENSG00000103269","cg02282892","Anastrozole"), polr_mod,xlevels=4), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000103269","cg05337753","Cyclophosphamide"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("ENSG00000103269","cg05337753","Doxorubicin"), polr_mod), style="stacked")


plot(Effect(focal.predictors = c("ENSG00000103269","ajcc_pathologic_tumor_stage.Stage.3","Doxorubicin"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000103269","cg02282892"), polr_mod), style="stacked")
plot(Effect(focal.predictors = c("cg05337753"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c("ENSG00000102796","ajcc_pathologic_tumor_stage.Stage.3","Doxorubicin"), polr_mod), style="stacked")

plot(Effect(focal.predictors = c('cg02282892','Doxorubicin','ajcc_pathologic_tumor_stage.Stage.I'), polr_mod), style="stacked")

plot(Effect(focal.predictors = c('cg05337753','ENSG00000103269','Doxorubicin'), polr_mod), style="stacked")
plot(Effect(focal.predictors = c('Doxorubicin','cg05337753','cg02282892'), polr_mod), style="stacked",
     xlevels = list(cg02282892=3, cg05337753=3, ENSG00000102796=3))
    
plot(Effect(focal.predictors = c("ENSG00000103269","ENSG00000102796","Doxorubicin"), polr_mod), style="stacked")

plot_model(polr_mod, type = "pred", terms = c("ENSG00000102796","Doxorubicin"))
plot_model(polr_mod, type = "pred", terms = c("ENSG00000103269","ajcc_pathologic_tumor_stage.Stage.I"))
plot_model(polr_mod, type = "pred", terms = c("ENSG00000103269","ENSG00000102796"))
plot_model(polr_mod, type = "pred", terms = c('hsa.mir.146a','Doxorubicin'))
plot_model(polr_mod, type = "pred", terms = c('ENSG00000102796','cg05337753'))


#  Doxorubicin*ajcc_pathologic_tumor_stage.Stage.I*ENSG00000103269*ENSG00000102796
                              + Doxorubicin*ENSG00000102796*cg02282892*ENSG00000100906
                              + Doxorubicin*ENSG00000102796*cg05337753*ENSG00000198832
                              + ENSG00000134917+
                              + hsa.mir.146a+ajcc_pathologic_tumor_stage.Stage.3+Cyclophosphamide + Tamoxifen
                              + Anastrozole+ Paclitaxel+ Docetaxel +Trastuzumab +Letrozole+  Fluorouracil+
                              + Exemestane+ Carboplatin+ Methotrexate

```

```{r}
summary(TOP_20_3c)
```

```{r}
library(broom)

clm_mod <- clm(as.factor(PFIbucket) ~ Doxorubicin*ajcc_pathologic_tumor_stage.Stage.I*ENSG00000103269*ENSG00000102796
                              + Doxorubicin*ENSG00000102796*cg02282892*ENSG00000100906
                              + Doxorubicin*ENSG00000102796*cg05337753*ENSG00000198832
                              + ENSG00000134917+
                              + hsa.mir.146a+ajcc_pathologic_tumor_stage.Stage.3+Cyclophosphamide + Tamoxifen
                              + Anastrozole+ Paclitaxel+ Docetaxel +Trastuzumab +Letrozole+  Fluorouracil+
                              + Exemestane+ Carboplatin+ Methotrexate,
         data = TOP_20_3c_polr_sc)
  tidy(clm_mod)
  tidy(clm_mod, conf.int = TRUE)
  write.csv(tidy(clm_mod, conf.int = TRUE, conf.type = "Wald", exponentiate = TRUE),'polr_results.csv')

  #Epirubicin+ 
```



```{r}

confusionMatrix(TOP_20_3c$PFIbucket,predict(int_mod, data = TOP_20_3c, type = 'class'))

```




#Read PC components

```{r}
omics_train<-read.csv("/Users/samiaferoze/Downloads/omics_pcs_train.csv")
omics_test<-read.csv("/Users/samiaferoze/Downloads/omics_pcs_test.csv")
head(omics_test)
colnames(omics_train)[1]<-"X"
colnames(omics_test)[1]<-"X"
omics_set<-rbind(omics_train, omics_test)
colnames(omics_set_train_v1)[1]<-'X'
omics_set_train<-merge(var20,omics_train)
omics_set_test<-merge(var20,omics_test)
omics_set_train_v1<-omics_set_train[c(1:15,18,23,24,25,26,32:41)]
omics_set_test_v1<-omics_set_test[c(1:15,18,23,24,25,26,32:41)]
```

#Principal components with 3 class
```{r}
TOP_20_3c<-TOP_20[-c(3,27)]
colnames(TOP_20_3c)
pc_3class<-merge(omics_train, TOP_20_3c, by= "X")
colnames(pc_3class)
pc_3<-pc_3class[c(2:11,272:285,287,288,297)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFIbucket) ~.,
                     data = pc_3,
                     method = 'rf',
                     metric = 'Accuracy',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  confusionMatrix(rf_fit)
  plot(rf_fit)

```


#Principal components with 2 class 
```{r}
TOP_20_2pc<-TOP_20[-c(2,3,5:12)]
colnames(PC_2C)
PC_2C<-merge(omics_train,TOP_20_2pc, by = "X")
PC_2C<-PC_2C[c(2:11,272:285,287,288,302)]
control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(as.factor(PFI_2_bucket) ~.,
                     data = PC_2C,
                     method = 'rf',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
confusionMatrix(rf_fit)
  plot(rf_fit)
```


#Principal components with PFI time sqrt


```{r}
pc_time<-merge(omics_train, TOP_20_time[-c(2)], by = "X")

colnames(pc_time)

pc_time_sel<-pc_time[c(2:11,272:285,287,296,310)]

control <- trainControl(method='repeatedcv', 
                          number=15, 
                          repeats=10,
                          search = 'grid')
  
  
  tunegrid <- expand.grid(.mtry=1:5)
  rf_fit <- train(PFI.time.sqrt ~.,
                     data = pc_time_sel,
                     method = 'rf',
                     tuneLength  = 15,
                     tuneGrid = tunegrid,
                     trControl = control, importance = TRUE)
  
  #print(rf_fit)
  #plot(rf_fit)
  
  
  rf_fit
  confusionMatrix(rf_fit)
  plot(rf_fit)
```

